Load datasets
```{r}
individuals <- read.csv(file = "individuals_data.csv", header = TRUE, sep = ",")
diets <- read.csv(file = "diets_data.csv", header = TRUE, sep = ",")
dryfishweights <- read.csv(file = "dryfishweights_data.csv", header = TRUE, sep = ",")

```


Modelling
Models for: Individual treatments and across treatments

TL vs weight
Liver weight vs TL
All factors of Individuals (TL, Wt, Liver Weight, Eviscerated weight, condition factor, weight difference, % viscera, HSI)

```{r}

```


Anova's
Anova's for: Across treatments

All factors for diets (Growth Rate, SGR, Average weight, Average TL, FCR, Liver weight, Eviscerated weight, condition factor, weight diff, % viscera, HSI)
All factors for Fish weights (% H20, Dry Matter, Body Weight)
Justin sampling average weight and individual weights from my sampling for whole fish and muscle for each diet

```{r}
library(car)

anovagrowthrate <- Anova(diets$growthrategpday ~ diets$diet)
anovasgr <- Anova(diets$sgr ~ diets$diet)
anovaavewt <- Anova(diets$avewt ~ diets$diet)
anovafcr <- Anova(diets$fcr ~ diets$diet)
anovaliverwt <- Anova(diets$liverwt ~ diets$diet)
anovaevisceratedwt <- Anova(diets$evisceratedwt ~ diets$diet)
anovacf <- Anova(diets$cfgperday ~ diets$diet)
anovawtdiff <- Anova(diets$wtdiffgrams ~ diets$diet)
anovapercentviscera <- Anova(diets$percentviscera ~ diets$diet)
anovahis <- Anova(diets$his ~ diets$diet)
```


T tests
T tests for: Justin sampling average weight and individual weights from my sampling for whole fish and muscle for each diet
```{r}

```
