Load datasets
```{r}
individuals <- read.csv(file = "individuals_data.csv", header = TRUE, sep = ",")
diets <- read.csv(file = "diets_data.csv", header = TRUE, sep = ",")
dryfishweights <- read.csv(file = "dryfishweights_data.csv", header = TRUE, sep = ",")

```


Modelling
Models for: Individual treatments and across treatments

TL vs weight
Liver weight vs TL
All factors of Individuals (TL, Wt, Liver Weight, Eviscerated weight, condition factor, weight difference, % viscera, HSI)

```{r}

```


Anova's
Anova's for: Across treatments

All factors for diets (Growth Rate, SGR, Average weight, Average TL, FCR, Liver weight, Eviscerated weight, condition factor, weight diff, % viscera, HSI)
All factors for Fish weights (% H20, Dry Matter, Body Weight)
Justin sampling average weight and individual weights from my sampling for whole fish and muscle for each diet

```{r}
anovaGrowthRate <- anova()
```


T tests
T tests for: Justin sampling average weight and individual weights from my sampling for whole fish and muscle for each diet
```{r}

```
