Load datasets
```{r}
individuals <- read.csv("./CSV Data Sheets/individuals_data.csv", header = TRUE)
individuals$diet <- as.factor(individuals$diet)

diets <- read.csv(file = "./CSV Data Sheets/diets_data.csv", header = TRUE)
dryfishweights <- read.csv(file = "./CSV Data Sheets/dryfishweights_data.csv", header = TRUE)
tankweights <- read.csv(file = "./CSV Data Sheets/tankweights_data.csv", header = TRUE)
allfish <- read.csv(file = "./CSV Data Sheets/allfish_data.csv", header = TRUE)

metabolomics <- read.csv(file = "./CSV Data Sheets/metabolomics_data.csv", header = TRUE)
proximates <- read.csv(file = "./CSV Data Sheets/proximates_data.csv", header = TRUE)

```


Plot Data
```{r}
plot(individuals$wt ~ individuals$tlmm, xlab = "Individual Total Length (mm)", ylab = "Individual Weight (g)", main = "Individual Weight vs Length Relationship")
lm01 <- lm(individuals$wt ~ individuals$tlmm)
abline(lm01, col = "blue")
summary(lm01)

plot(individuals$liverwt, individuals$tlmm)
plot(individuals$liverwt, individuals$wt)
plot(individuals$hsi, individuals$tlmm)
plot(individuals$hsi, individuals$wt)
plot(individuals$conditionfactor ~ individuals$tlmm)
plot(individuals$conditionfactor ~ individuals$wt)



boxplot(individuals$wt ~ individuals$diet)
boxplot(individuals$liverwt ~ individuals$diet)
boxplot(individuals$percentviscera ~ individuals$diet)
boxplot(individuals$tlmm ~ individuals$diet)
boxplot(individuals$evisceratedwt ~ individuals$diet)
boxplot(individuals$conditionfactor ~ individuals$diet)
boxplot(individuals$hsi ~ individuals$diet)
boxplot(individuals$wtdiff ~ individuals$diet)


boxplot(allfish$wt ~ allfish$diet)
boxplot(allfish$tlmm ~ allfish$diet)

```



Modelling
Models for: Individual treatments and across treatments

TL vs weight
Liver weight vs TL
All factors of Individuals (TL, Wt, Liver Weight, Eviscerated weight, condition factor, weight difference, % viscera, HSI)

```{r}
lm1 <- lm(individuals$wt ~ individuals$tlmm)
lmhsi <- lm(individuals$liverwt ~ individuals$tlmm)

```


Anova's
Anova's for: Across treatments

All factors for diets (Growth Rate, SGR, Average weight, Average TL, FCR, Liver weight, Eviscerated weight, condition factor, weight diff, % viscera, HSI)
All factors for Fish weights (% H20, Dry Matter, Body Weight)
Justin sampling average weight and individual weights from my sampling for whole fish and muscle for each diet

```{r}
library(car)

anovagrowthrate <- Anova(diets$growthrategpday ~ diets$diet)
anovasgr <- Anova(diets$sgr ~ diets$diet)
anovaavewt <- Anova(diets$avewt ~ diets$diet)
anovafcr <- Anova(diets$fcr ~ diets$diet)
anovaliverwt <- Anova(diets$liverwt ~ diets$diet)
anovaevisceratedwt <- Anova(diets$evisceratedwt ~ diets$diet)
anovacf <- Anova(diets$cfgperday ~ diets$diet)
anovawtdiff <- Anova(diets$wtdiffgrams ~ diets$diet)
anovapercentviscera <- Anova(diets$percentviscera ~ diets$diet)
anovahsi <- Anova(diets$hsi ~ diets$diet)

#individuals

#hsi linear model
lmhsi <- lm(individuals$hsi ~ individuals$diet, data = individuals)
summary(lmhsi)
aovhsi <- aov(individuals$hsi ~ individuals$diet, data = individuals)
summary(aovhsi)
aovhsi
posthoc1 <- TukeyHSD(x=aovhsi, 'individuals$diet', conf.level=0.99)
posthoc1

#liverwt linear model
lmliverwt <- lm(individuals$liverwt ~ individuals$diet)
summary(lmliverwt)
aovliverwt <- aov(individuals$liverwt ~ individuals$diet)
summary(aovliverwt)
posthoc2 <- TukeyHSD(x=aovliverwt, 'individuals$diet', conf.level=0.99)
```


T tests
T tests for: Justin sampling average weight and individual weights from my sampling for whole fish and muscle for each diet
```{r}

```


PCA Coding for Metabolomics Analysis
```{r}

```


ANOVA's for Proximate Analysis and bar plots of proximates
```{r}
protein <- table(proximates$protein)
barplot(protein, main="Protein comparison among diet treatments", 
   xlab="Diets")

fat <- table(proximates$fat)
barplot(fat, main="Fat comparison among diet treatments", 
   xlab="Diets")

carb <- table(proximates$carb)
barplot(carb, main="Carbohydrate comparison among diet treatments", 
   xlab="Diets")


```

















