Load datasets and set factors as needed
```{r}
# Read in data sets, need to import first to read; download from repo, then import to environment

individuals <- individuals_data
individuals <- read.csv(file = "./data/individuals_data.csv", header = TRUE)
individuals$diet <- as.factor(individuals$diet)
individuals$diet = factor(individuals$diet,c("FSHSQ","FSH","FSQ","SHSQ","F","SH","SQ","PELL"))

dryfishweights <- read.csv(file = "./data/dryfishweights_data.csv", header = TRUE)

allfish <- allfish_data
allfish <- read.csv(file = "./data/allfish_data.csv", header = TRUE)
allfish$diet = factor(allfish$diet,c("FSHSQ","FSH","FSQ","SHSQ","F","SH","SQ","PELL"))

justinwt <- justinwt_data
justinwt <- read.csv("./data/justinwt_data.csv", header = TRUE)
justinwt$diet = factor(justinwt$diet,c("FSHSQ","FSH","FSQ","SHSQ","F","SH","SQ","PELL"))

metabolomics <- metabolomics_data
metabolomics <- read.csv(file = "./data/metabolomics_data.csv", header = TRUE)

proximates <- proximates_data
proximates <- read.csv(file = "./data/proximates_data.csv", header = TRUE)

water <- weeklywaterquality_data
water <- read.csv(file = "./data/weeklywaterquality_data", header = TRUE)

daily <- dailywaterquality_data
daily <- read.csv(file = "./data/dailywaterquality_data", header = TRUE)

bucket <- bucketexample2_data
bucket <- read.csv(file = "./data/bucketexample2_data", header = TRUE)

bucket.env <- bucketexample2_data_env
bucket.env <- read.csv(file = "./data/bucketexample2_data.env.csv", header = TRUE)

fcr <- fcr_data
fcr <- read.csv(file = "./data/fcr_data.csv", header = TRUE)
fcr$diet <- as.factor(fcr$diet)
fcr$diet = factor(fcr$diet,c("FSHSQ","FSH","FSQ","SHSQ","F","SH","SQ","PELL"))
```


Plot Data; this is relevant data to my thesis work; a couple models as well
```{r}
plot(individuals$wt ~ individuals$tlmm, xlab = "Individual Total Length (mm)", ylab = "Individual Weight (g)", main = "Individual Weight vs Length Relationship", pch = 16, las = 1)
lm01 <- lm(individuals$wt ~ individuals$tlmm)
abline(lm01, col = "blue")
summary(lm01)

#log transform data for length weight relationship
plot(log(individuals$wt) ~ log(individuals$tlmm), xlab = "log(Individual Total Length (mm))", ylab = "log(Individual Weight (g)", main = "Individual Weight vs Length Relationship", pch = 16, las = 1)
lmlog <- lm(log(individuals$wt) ~ log(individuals$tlmm))
abline(lmlog, col = "blue")
summary(lmlog)

# Exponential Model
sortedindividuals <- individuals[order(individuals$tlmm),]
theta.0 <- min(sortedindividuals$wt) * 0.5
model.0 <- lm(log(sortedindividuals$wt - theta.0) ~ sortedindividuals$wt, data = sortedindividuals)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start
expmod <- nls(sortedindividuals$wt ~ alpha * exp(beta*sortedindividuals$tlmm) + theta, data = sortedindividuals, start = start)
summary(expmod)
plot(sortedindividuals$wt ~ sortedindividuals$tlmm, xlab = "Individual Total Length (mm)", ylab = "Individual Weight (g)", main = "Individual Weight vs Length Relationship", pch = 16, las = 1)
lines(sortedindividuals$tlmm, predict(expmod, list(sortedindividuals$tlmm)), col = 'blue', lwd = 1)
AIC(lm01)
AIC(expmod)



plot(individuals$tlmm, individuals$liverwt, xlab = "Individual Total Length (mm)", ylab = "Individual Liver Weight (g)", main = "Individual Total Length vs Liver Weight HSI", pch = 16, las = 1)
lm02 <- lm(individuals$liverwt ~ individuals$tlmm)
abline(lm02, col = "blue")
summary(lm02)
#taking out diet 8 makes model much better; shows difference in pellets w/natural diets
df2 <- data.frame(individuals$diet[individuals$diet != 8], individuals$tlmm[individuals$diet != 8], individuals$liverwt[individuals$diet != 8])
df2
plot(df2$individuals.tlmm.individuals.diet....8.,df2$individuals.liverwt.individuals.diet....8.)
lmdf2 <- lm(df2$individuals.liverwt.individuals.diet....8. ~ df2$individuals.tlmm.individuals.diet....8.)
abline(lmdf2, col = "blue")
summary(lmdf2)

plot(individuals$wt, individuals$liverwt, xlab = "Individual Weight (g)", ylab = "Individual Liver Weight (g)", main = "Individual Weight vs Liver Weight Relationship", pch = 16, las = 1)
lm03 <- lm(individuals$liverwt ~ individuals$wt)
abline(lm03, col = "blue")
summary(lm03)
#taking out diet 8 makes model much better; shows difference in pellets w/natural diets
df3 <- data.frame(individuals$diet[individuals$diet != 8], individuals$wt[individuals$diet != 8], individuals$liverwt[individuals$diet != 8])
df3
plot(df3$individuals.wt.individuals.diet....8.,df3$individuals.liverwt.individuals.diet....8.)
lmdf3 <- lm(df$individuals.liverwt.individuals.diet....8. ~ df$individuals.wt.individuals.diet....8.)
abline(lmdf3, col = "blue")
summary(lmdf3)


# Show data as boxplots to show variation between diets

boxplot(justinwt$weight ~ justinwt$diet, xlab = "Diet", ylab = "Average Fish Weight (g)", main = "Average Fish Weight Across Diets", ylim = c(0,200), par(cex.axis=0.70))

boxplot(individuals$wt ~ individuals$diet, xlab = "Diet", ylab = "Fish Weight (g)", main = "Average Fish Weight Across Diets", ylim = c(0,200), las = 1, par(cex.axis=0.70))

boxplot(individuals$liverwt ~ individuals$diet, xlab = "Diet", ylab = "Liver Weight (g)", main = "Average Fish Liver Weight Across Diets", las = 1, par(cex.axis=0.70))

boxplot(individuals$percentviscera ~ individuals$diet, xlab = "Diet", ylab = "Percent Viscera (%)", main = "Average Fish Percent Viscera Across Diets", ylim = c(0,16), las = 1, par(cex.axis=0.70))

boxplot(individuals$tlmm ~ individuals$diet, xlab = "Diet", ylab = "Total Length (mm)", main = "Average Fish Total Length Across Diets", las = 1, par(cex.axis=0.70))

boxplot(individuals$evisceratedwt ~ individuals$diet, xlab = "Diet", ylab = "Eviscerated Weight (g)", main = "Average Fish Eviscerated Weights Across Diets", las = 1, par(cex.axis=0.70))

boxplot(individuals$conditionfactor ~ individuals$diet, xlab = "Diet", ylab = "Condition Factor (g/cm^3)", main = "Average Fish Condition Factor Across Diets", las = 1, par(cex.axis=0.70))

boxplot(individuals$hsi ~ individuals$diet, xlab = "Diet", ylab = "HSI", main = "Average Fish Heposomatic Index Across Diets", las = 1, par(cex.axis=0.70))

boxplot(individuals$wtdiff ~ individuals$diet, xlab = "Diet", ylab = "Weight Difference (g)", main = "Average Fish Total Weight - Eviscerated Weight", ylim = c(0,20), las = 1, par(cex.axis=0.70))


boxplot(allfish$wt ~ allfish$diet, xlab = "Diet", ylab = "Average Fish Weight (g)", main = "Average Fish Weight Across Diets", ylim = c(0,250), las = 1, par(cex.axis=0.70))

boxplot(allfish$tlmm ~ allfish$diet, xlab = "Diet", ylab = "Average Total Length (mm)", main = "Average Fish Total Length Across Diets", ylim = c(0,300), las = 1, par(cex.axis=0.70))


boxplot(fcr$`wet fcr ave.` ~ fcr$diet, xlab = "Diet", ylab = "wet:wet FCR", main = "FCR of wet feed:wet biomass accross diets", ylim = c(0,8), las = 1, par(cex.axis=0.70))

boxplot(fcr$`dry fcr ave.` ~ fcr$diet, xlab = "Diet", ylab = "dry:wet FCR", main = "FCR of dry feed:wet biomass accross diets", ylim = c(0,2), las = 1, par(cex.axis=0.70))
```



Mean weights from sampling all fish in all tanks (justin dataset), vs individuals samples and killed (individuals dataset), vs individuals sampled and killed and dried in oven (all fish dataset) to see if there are any glaring discrepancies
```{r}
#mean average fish weight my sampling only
mean(justinwt$weight[justinwt$diet == "FSHSQ"])
mean(justinwt$weight[justinwt$diet == "FSH"])
mean(justinwt$weight[justinwt$diet == "FSQ"])
mean(justinwt$weight[justinwt$diet == "SHSQ"])
mean(justinwt$weight[justinwt$diet == "F"])
mean(justinwt$weight[justinwt$diet == "SH"])
mean(justinwt$weight[justinwt$diet == "SQ"])
mean(justinwt$weight[justinwt$diet == "PELL"])

#mean average fish weight my sampling only
mean(individuals$wt[individuals$diet == "FSHSQ"])
mean(individuals$wt[individuals$diet == "FSH"])
mean(individuals$wt[individuals$diet == "FSQ"])
mean(individuals$wt[individuals$diet == "SHSQ"])
mean(individuals$wt[individuals$diet == "F"])
mean(individuals$wt[individuals$diet == "SH"])
mean(individuals$wt[individuals$diet == "SQ"])
mean(individuals$wt[individuals$diet == "PELL"])

#sd average fish weight my sampling only
sd(individuals$wt[individuals$diet == "FSHSQ"])
sd(individuals$wt[individuals$diet == "FSH"])
sd(individuals$wt[individuals$diet == "FSQ"])
sd(individuals$wt[individuals$diet == "SHSQ"])
sd(individuals$wt[individuals$diet == "F"])
sd(individuals$wt[individuals$diet == "SH"])
sd(individuals$wt[individuals$diet == "SQ"])
sd(individuals$wt[individuals$diet == "PELL"])

#mean average fish weight my sampling and drying
mean(allfish$wt[allfish$diet == "FSHSQ"])
mean(allfish$wt[allfish$diet == "FSH"])
mean(allfish$wt[allfish$diet == "FSQ"])
mean(allfish$wt[allfish$diet == "SHSQ"])
mean(allfish$wt[allfish$diet == "F"])
mean(allfish$wt[allfish$diet == "SH"])
mean(allfish$wt[allfish$diet == "SQ"])
mean(allfish$wt[allfish$diet == "PELL"])

```


Anova's and linear models and post hoc tests to determine statistical differences
Anova's for: Across treatments

All factors for individuals given diets ( SGR, Average weight, Average TL, FCR, Liver weight, Eviscerated weight, condition factor, weight diff, % viscera, HSI)
All factors for Fish weights (% H20, Dry Matter, Body Weight)

```{r}
#individuals

#hsi linear model
lmhsi <- lm(individuals$hsi ~ individuals$diet, data = individuals)
summary(lmhsi)
aovhsi <- aov(individuals$hsi ~ individuals$diet, data = individuals)
summary(aovhsi)
aovhsi
posthoc1 <- TukeyHSD(x=aovhsi, 'individuals$diet', conf.level=0.99)
posthoc1

#liverwt linear model
lmliverwt <- lm(individuals$liverwt ~ individuals$diet)
summary(lmliverwt)
aovliverwt <- aov(individuals$liverwt ~ individuals$diet)
aovliverwt
summary(aovliverwt)
posthoc2 <- TukeyHSD(x=aovliverwt, 'individuals$diet', conf.level=0.99)
posthoc2

#wt linear model
lmwt <- lm(individuals$wt ~ individuals$diet)
summary(lmwt)
aovwt <- aov(individuals$wt ~ individuals$diet)
aovwt
summary(aovwt)
posthoc3 <- TukeyHSD(x=aovwt, 'individuals$diet', conf.level=0.99)
posthoc3

#tlmm linear model
lmtlmm <- lm(individuals$tlmm ~ individuals$diet)
summary(lmtlmm)
aovtlmm <- aov(individuals$tlmm ~ individuals$diet)
aovtlmm
summary(aovtlmm)
posthoc4 <- TukeyHSD(x=aovtlmm, 'individuals$diet', conf.level=0.99)
posthoc4

#%viscera linear model
lmviscera <- lm(individuals$percentviscera ~ individuals$diet)
summary(lmviscera)
aovviscera <- aov(individuals$percentviscera ~ individuals$diet)
aovviscera
summary(aovviscera)
posthoc5 <- TukeyHSD(x=aovviscera, 'individuals$diet', conf.level=0.99)
posthoc5

#condition factor linear model
lmcf <- lm(individuals$conditionfactor ~ individuals$diet)
summary(lmcf)
aovcf <- aov(individuals$conditionfactor ~ individuals$diet)
aovcf
summary(aovcf)
posthoc6 <- TukeyHSD(x=aovcf, 'individuals$diet', conf.level=0.99)
posthoc6

#Wet feed:wet biomass linear model
lmfcrww <- lm(fcr$`wet fcr ave.` ~ fcr$diet)
summary(lmfcrww)
aovfcrww <- aov(fcr$`wet fcr ave.` ~ fcr$diet)
aovfcrww
summary(aovfcrww)
posthoc7 <- TukeyHSD(x=aovfcrww, 'fcr$diet', conf.level=0.99)
posthoc7

#Dry feed:wet biomass linear model
lmfcrdw <- lm(fcr$`dry fcr ave.` ~ fcr$diet)
summary(lmfcrdw)
aovfcrdw <- aov(fcr$`dry fcr ave.` ~ fcr$diet)
summary(aovfcrdw)
posthoc8 <- TukeyHSD(x=aovfcrdw, 'fcr$diet', conf.level=0.99)
posthoc8
```



PCA Example with bucket data from Fabio; this is to show what I want to do with my data to determine statistical differences among metabolomes
```{r}
bucket.env <- bucketexample2_data_env

library(vegan)
bucket <- t(bucketexample2_data)
bucket_pca <- rda(bucket)
bucket_pca
plot(bucket_pca)
str(bucket_pca)
bucket_pca$
bucket_pca$tot.chi
bucket_pca$CA$eig
sum(bucket_pca$CA$eig)
round(bucket_pca$CA$eig / bucket_pca$tot.chi, 2)
biplot(bucket_pca)
cleanplot.pca(bucket_pca)

ordiplot(bucket_pca, display = 'sp')
orditorp(bucket_pca, display = 'sp')

# Negative numbers may affect results of NMDS!
bucket_mds <- metaMDS(bucket)
plot(bucket_mds)

# RDA number 2
 rda_bucket <- rda(bucket, bucket.env)
 rda_bucket

 RsquareAdj(rda_bucket)
 
 plot(rda_bucket, type='n', scaling=1)
orditorp(rda_bucket, display='sp', cex=0.5, scaling=1, col='blue')
text(rda_bucket, display='cn', col='red')

bucket.env$diet
levels(bucket.env$diet)

cca_bucket <- cca(bucket ~ ., data = bucket.env)
cca_bucket
RsquareAdj(cca_bucket, 100)
anova(cca_bucket, permutations = 999)
anova(cca_bucket, by='margin', permutations = 999)
plot(cca_bucket, type='n', scaling=1)
orditorp(cca_bucket, display='sp', cex=0.5, scaling=1, col='blue')
text(cca_bucket, display='bp', col='red')

```

PCA Coding for Metabolomics Analysis
RDA indirect ordination and then do a direct ordination;
```{r}
#This code will not have any data with it now; just the template for now
met_pca <- rda(metabolomics, scale = TRUE)
met_pca
str(met_pca)
met_pca$
met_pca$tot.chi
met_pca$CA$eig
sum(met_pca$CA$eig)
round(met_pca$CA$eig / met_pca$tot.chi, 2)
plot(met_pca)
biplot(met_pca)
cleanplot.pca(met_pca)
ordiplot(met_pca, display = 'met')
orditorp(met_pca, display = 'met')

met_mds <- metaMDS(metabolomics)
plot(met_mds)

plot(met_mds, type='n')
 text(met_mds, 'met', cex=.5)
 # generate vector of colors 
 color_vect = rev(terrain.colors(6))[-1]
 points(met_mds, 'diet', pch=19, 
        col=color_vect[met.env$diet])
 legend('topright', paste("diet =", 1:5, sep=''), 
        col=color_vect, pch=19)
 
 # RDA number 2
 rda_met <- rda(met, met.env)
 rda_met

 RsquareAdj(rda_met)
 
 plot(rda_met, type='n', scaling=1)
orditorp(rda_met, display='met', cex=0.5, scaling=1, col='blue')
text(rda_met, display='met', col='red')
```


ANOVA's for Proximate Analysis and bar plots of proximates
```{r}
#This code will not have any data with it now; just the template for now
protein <- table(proximates$protein)
barplot(protein, main="Protein comparison among diet treatments", 
   xlab="Diets")

fat <- table(proximates$fat)
barplot(fat, main="Fat comparison among diet treatments", 
   xlab="Diets")

carb <- table(proximates$carb)
barplot(carb, main="Carbohydrate comparison among diet treatments", 
   xlab="Diets")


```


Weekly Water Quality Range, mean, stdev for data table
```{r}
mean(water$`Ammonia mg/L`)
sd(water$`Ammonia mg/L`)
range(water$`Ammonia mg/L`)
mean(water$`Nitrite mg/L`, na.rm = TRUE)
sd(water$`Nitrite mg/L`, na.rm = TRUE)
range(water$`Nitrite mg/L`, na.rm = TRUE)
mean(water$`Nitrate mg/L`, na.rm = TRUE)
sd(water$`Nitrate mg/L`, na.rm = TRUE)
range(water$`Nitrate mg/L`, na.rm = TRUE)
```


Daily Water Quality Range, mean, stdev for data table
```{r}
mean(daily$temp)
sd(daily$temp)
range(daily$temp)
mean(daily$do, na.rm = TRUE)
sd(daily$do, na.rm = TRUE)
range(daily$do, na.rm = TRUE)
mean(daily$sal)
sd(daily$sal)
range(daily$sal)
mean(daily$pH)
sd(daily$pH)
range(daily$pH)


```











