Load datasets and set factors as needed
```{r}
# Read in data sets; download from repo, then import to environment; proximates_data and metabolomics_data are not used. The shutdowns affected my ability to get the data, but I am leaving them here so I have the code in the future.

#1.
individuals <- individuals_data
individuals$diet <- as.factor(individuals$diet)
individuals$diet = factor(individuals$diet,c("FSHSQ","FSH","FSQ","SHSQ","F","SH","SQ","PELL"))

#2.
dryfishweights <- read.csv(file = "./data/dryfishweights_data.csv", header = TRUE)

#3.
allfish <- allfish_data
allfish$diet = factor(allfish$diet,c("FSHSQ","FSH","FSQ","SHSQ","F","SH","SQ","PELL"))

#4.
justinwt <- justinwt_data
justinwt$diet = factor(justinwt$diet,c("FSHSQ","FSH","FSQ","SHSQ","F","SH","SQ","PELL"))

#5.
metabolomics <- metabolomics_data

#6.
proximates <- proximates_data

#7.
water <- weeklywaterquality_data

#8
daily <- dailywaterquality_data

#9.
bucket <- bucketexample2_data

#10.
bucket.env <- bucketexample2_data_env

#11.
fcr <- fcr_data
fcr$diet <- as.factor(fcr$diet)
fcr$diet = factor(fcr$diet,c("FSHSQ","FSH","FSQ","SHSQ","F","SH","SQ","PELL"))
```


Plot Data; this is relevant data to my thesis work; a couple models as well
```{r}
qqnorm(individuals$wt)
qqnorm(individuals$tlmm)
#individuals$wt and individuals$tlmm are normal, do not violate anova


#Plot significant data to put into presentation and Thesis; tiff files so they are in much better resolution

#1. Plot of weight and total length not log transformed
tiff("wt~tlmm.tiff", width = 6, height = 4, units = 'in', res = 300)
plot(individuals$wt ~ individuals$tlmm, xlab = "Individual Total Length (mm)", ylab = "Individual Weight (g)", main = "Individual Weight vs Length Relationship", pch = 16, las = 1)
lm01 <- lm(individuals$wt ~ individuals$tlmm)
abline(lm01, col = "blue")
summary(lm01)
lm001 <- lm(individuals$wt ~ individuals$tlmm) # Make plot
dev.off()

#2. Plot of weight and total length log transformed
tiff("log(wt~tlmm).tiff", width = 6, height = 4, units = 'in', res = 300)
plot(log(individuals$wt) ~ log(individuals$tlmm), xlab = "log(Individual Total Length (mm))", ylab = "log(Individual Weight (g)", main = "Individual Weight vs Length Relationship", pch = 16, las = 1)
lmlog <- lm(log(individuals$wt) ~ log(individuals$tlmm))
abline(lmlog, col = "blue")
summary(lmlog)
lm002 <- lm(log(individuals$wt) ~ log(individuals$tlmm)) # Make plot
dev.off()

#3. Plot of total length and liver weight
tiff("tlmm~liverwt.tiff", width = 5, height = 4, units = 'in', res = 300)
plot(individuals$tlmm, individuals$liverwt, xlab = "Individual Total Length (mm)", ylab = "Individual Liver Weight (g)", main = "Individual Total Length vs Liver Weight HSI", pch = 16, las = 1)
lm02 <- lm(individuals$liverwt ~ individuals$tlmm)
abline(lm02, col = "blue")
summary(lm02)
lm003 <- lm(individuals$liverwt ~ individuals$tlmm) # Make plot
dev.off()

#4. Plot of HSI (weight and liver weight
tiff("HSI.tiff", width = 5, height = 4, units = 'in', res = 300)
plot(individuals$wt, individuals$liverwt, xlab = "Individual Weight (g)", ylab = "Individual Liver Weight (g)", main = "Individual Weight vs Liver Weight Relationship", pch = 16, las = 1)
lm03 <- lm(individuals$liverwt ~ individuals$wt)
abline(lm03, col = "blue")
summary(lm03)
lm004 <- lm(individuals$liverwt ~ individuals$wt) # Make plot
dev.off()



# Boxplots showing differences in diet treatments given a parameter

#1. Average Fish Weight
tiff("Average Fish Weight.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(justinwt$weight ~ justinwt$diet, xlab = "Diet", ylab = "Average Fish Weight (g)", main = "Average Fish Weight Across Diets", ylim = c(0,200), las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#2. Specific Growth Rate
tiff("SGR.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(justinwt$sgr ~ justinwt$diet, xlab = "Diet", ylab = "SGR (%/day)", main = "Specific Growth Rate Across Diets", ylim = c(0,2.5), las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#3. Liver Weight
tiff("Liver Weight.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(individuals$liverwt ~ individuals$diet, xlab = "Diet", ylab = "Liver Weight (g)", main = "Average Fish Liver Weight Across Diets", las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#4. Liver Weight
tiff("Percent Viscera.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(individuals$percentviscera ~ individuals$diet, xlab = "Diet", ylab = "Percent Viscera (%)", main = "Average Fish Percent Viscera Across Diets", ylim = c(0,16), las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#5. Total Length
tiff("Total Length.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(individuals$tlmm ~ individuals$diet, xlab = "Diet", ylab = "Total Length (mm)", main = "Average Fish Total Length Across Diets", las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#6. Eviscerated Weight
tiff("Eviscerated Weight.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(individuals$evisceratedwt ~ individuals$diet, xlab = "Diet", ylab = "Eviscerated Weight (g)", main = "Average Fish Eviscerated Weights Across Diets", las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#7. Condition Factor
tiff("Condition Factor.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(individuals$conditionfactor ~ individuals$diet, xlab = "Diet", ylab = "Condition Factor (g/cm^3)", main = "Average Fish Condition Factor Across Diets", las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#8. Hepatosomatic Index
tiff("Hepatosomatic Index.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(individuals$hsi ~ individuals$diet, xlab = "Diet", ylab = "HSI (g/mm)*100", main = "Average Fish Heposomatic Index Across Diets", las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#9. Average Fish Total Weight - Eviscerated Weight
tiff("Weight Diff.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(individuals$wtdiff ~ individuals$diet, xlab = "Diet", ylab = "Weight Difference (g)", main = "Average Fish Total Weight - Eviscerated Weight", ylim = c(0,20), las = 1,par(cex.axis=0.70)) # Make plot
dev.off()

#10. FCR Dry:Wet Biomass
tiff("FCR Dry.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(fcr$`wet fcr ave.` ~ fcr$diet, xlab = "Diet", ylab = "wet:wet FCR", main = "FCR of wet feed:wet biomass accross diets", ylim = c(0,8), las = 1, par(cex.axis=0.70)) # Make plot
dev.off()

#11. FCR Wet:Wet Biomass
tiff("FCR Wet.tiff", width = 5, height = 4, units = 'in', res = 300)
boxplot(fcr$`dry fcr ave.` ~ fcr$diet, xlab = "Diet", ylab = "dry:wet FCR", main = "FCR of dry feed:wet biomass accross diets", ylim = c(0,2), las = 1, par(cex.axis=0.70)) # Make plot
dev.off()
```



Mean weights from sampling all fish in all tanks (justin dataset), vs individuals samples and killed (individuals dataset), vs individuals sampled and killed and dried in oven (all fish dataset) to see if there are any glaring differences in averages
```{r}
#mean average fish weight from Justin weighting each tank on the final day of sampling; includes every fish (n = ~44 to 48 each diet)
mean(justinwt$weight[justinwt$diet == "FSHSQ"])
mean(justinwt$weight[justinwt$diet == "FSH"])
mean(justinwt$weight[justinwt$diet == "FSQ"])
mean(justinwt$weight[justinwt$diet == "SHSQ"])
mean(justinwt$weight[justinwt$diet == "F"])
mean(justinwt$weight[justinwt$diet == "SH"])
mean(justinwt$weight[justinwt$diet == "SQ"])
mean(justinwt$weight[justinwt$diet == "PELL"])

#mean average fish weight from measuring individual fish during dissections on last day; (n = 9 fish per diet)
mean(individuals$wt[individuals$diet == "FSHSQ"])
mean(individuals$wt[individuals$diet == "FSH"])
mean(individuals$wt[individuals$diet == "FSQ"])
mean(individuals$wt[individuals$diet == "SHSQ"])
mean(individuals$wt[individuals$diet == "F"])
mean(individuals$wt[individuals$diet == "SH"])
mean(individuals$wt[individuals$diet == "SQ"])
mean(individuals$wt[individuals$diet == "PELL"])

#sd average fish weight my sampling only
sd(individuals$wt[individuals$diet == "FSHSQ"])
sd(individuals$wt[individuals$diet == "FSH"])
sd(individuals$wt[individuals$diet == "FSQ"])
sd(individuals$wt[individuals$diet == "SHSQ"])
sd(individuals$wt[individuals$diet == "F"])
sd(individuals$wt[individuals$diet == "SH"])
sd(individuals$wt[individuals$diet == "SQ"])
sd(individuals$wt[individuals$diet == "PELL"])

#mean average fish weight my sampling and drying (n = 19 per diet)
mean(allfish$wt[allfish$diet == "FSHSQ"])
mean(allfish$wt[allfish$diet == "FSH"])
mean(allfish$wt[allfish$diet == "FSQ"])
mean(allfish$wt[allfish$diet == "SHSQ"])
mean(allfish$wt[allfish$diet == "F"])
mean(allfish$wt[allfish$diet == "SH"])
mean(allfish$wt[allfish$diet == "SQ"])
mean(allfish$wt[allfish$diet == "PELL"])

```


Anova's and linear models and post hoc tests to determine statistical differences across diets
```{r}
#individuals

#hsi linear model; models hepatasomatic index of diets and compares to see if there are differences
lmhsi <- lm(individuals$hsi ~ individuals$diet, data = individuals)
summary(lmhsi)
aovhsi <- aov(individuals$hsi ~ individuals$diet, data = individuals)
summary(aovhsi)
aovhsi
posthoc1 <- TukeyHSD(x=aovhsi, 'individuals$diet', conf.level=0.99)
posthoc1

#liverwt linear model; models final liver weights in grams of diets and compares to see if there are differences
lmliverwt <- lm(individuals$liverwt ~ individuals$diet)
summary(lmliverwt)
aovliverwt <- aov(individuals$liverwt ~ individuals$diet)
aovliverwt
summary(aovliverwt)
posthoc2 <- TukeyHSD(x=aovliverwt, 'individuals$diet', conf.level=0.99)
posthoc2

#wt linear model; models final weight in grams of diets and compares to see if there are differences
lmwt <- lm(individuals$wt ~ individuals$diet)
summary(lmwt)
aovwt <- aov(individuals$wt ~ individuals$diet)
aovwt
summary(aovwt)
posthoc3 <- TukeyHSD(x=aovwt, 'individuals$diet', conf.level=0.99)
posthoc3

#tlmm linear model; models final Total Length in mm of diets and compares to see if there are differences
lmtlmm <- lm(individuals$tlmm ~ individuals$diet)
summary(lmtlmm)
aovtlmm <- aov(individuals$tlmm ~ individuals$diet)
aovtlmm
summary(aovtlmm)
posthoc4 <- TukeyHSD(x=aovtlmm, 'individuals$diet', conf.level=0.99)
posthoc4

#%viscera linear model; models percent viscera of total body weight of diets and compares to see if there are differences
lmviscera <- lm(individuals$percentviscera ~ individuals$diet)
summary(lmviscera)
aovviscera <- aov(individuals$percentviscera ~ individuals$diet)
aovviscera
summary(aovviscera)
posthoc5 <- TukeyHSD(x=aovviscera, 'individuals$diet', conf.level=0.99)
posthoc5

#condition factor linear model; models condition factor of diets and compares to see if there are differences
lmcf <- lm(individuals$conditionfactor ~ individuals$diet)
summary(lmcf)
aovcf <- aov(individuals$conditionfactor ~ individuals$diet)
aovcf
summary(aovcf)
posthoc6 <- TukeyHSD(x=aovcf, 'individuals$diet', conf.level=0.99)
posthoc6

#Wet feed:wet biomass linear model; models the wet feed fed:wet biomass gained of diets and compares to see if there are differences
lmfcrww <- lm(fcr$`wet fcr ave.` ~ fcr$diet)
summary(lmfcrww)
aovfcrww <- aov(fcr$`wet fcr ave.` ~ fcr$diet)
aovfcrww
summary(aovfcrww)
posthoc7 <- TukeyHSD(x=aovfcrww, 'fcr$diet', conf.level=0.99)
posthoc7

#Dry feed:wet biomass linear model; models the dry feed fed:wet biomass gained of diets and compares to see if there are differences
lmfcrdw <- lm(fcr$`dry fcr ave.` ~ fcr$diet)
summary(lmfcrdw)
aovfcrdw <- aov(fcr$`dry fcr ave.` ~ fcr$diet)
summary(aovfcrdw)
posthoc8 <- TukeyHSD(x=aovfcrdw, 'fcr$diet', conf.level=0.99)
posthoc8

#Specific Growth Rate linear model; models specific growth rate of diets and compares to see if there are differences
lmsgr <- lm(justinwt$sgr ~ justinwt$diet)
summary(lmsgr)
aovsgr <- aov(justinwt$sgr ~ justinwt$diet)
summary(aovsgr)
posthoc8 <- TukeyHSD(x=aovsgr, 'justinwt$diet', conf.level=0.99)
posthoc8
```


PCA Example with bucket data from Fabio; this is to show what I want to do with my data to determine statistical differences among metabolomes
```{r}
bucket.env <- bucketexample2_data_env

library(vegan)
bucket <- t(bucketexample2_data)
bucket_pca <- rda(bucket)
bucket_pca
plot(bucket_pca)
str(bucket_pca)
bucket_pca$
bucket_pca$tot.chi
bucket_pca$CA$eig
sum(bucket_pca$CA$eig)
round(bucket_pca$CA$eig / bucket_pca$tot.chi, 2)
biplot(bucket_pca)
cleanplot.pca(bucket_pca)

ordiplot(bucket_pca, display = 'sp')
orditorp(bucket_pca, display = 'sp')

# Negative numbers may affect results of NMDS!
bucket_mds <- metaMDS(bucket)
plot(bucket_mds)

 rda_bucket <- rda(bucket, bucket.env)
 rda_bucket

 RsquareAdj(rda_bucket)
 
 plot(rda_bucket, type='n', scaling=1)
orditorp(rda_bucket, display='sp', cex=0.5, scaling=1, col='blue')
text(rda_bucket, display='cn', col='red')

bucket.env$diet
levels(bucket.env$diet)

cca_bucket <- cca(bucket ~ ., data = bucket.env)
cca_bucket
RsquareAdj(cca_bucket, 100)
anova(cca_bucket, permutations = 999)
anova(cca_bucket, by='margin', permutations = 999)
plot(cca_bucket, type='n', scaling=1)
orditorp(cca_bucket, display='sp', cex=0.5, scaling=1, col='blue')
text(cca_bucket, display='bp', col='red')

```


PCA Coding for Metabolomics Analysis
RDA indirect ordination and then do a direct ordination;
```{r}
#This code chunk will not have any data with it now; just the template for now; see above code chunk for what this should look similar to with data

met_pca <- rda(metabolomics, scale = TRUE)
met_pca
str(met_pca)
met_pca$
met_pca$tot.chi
met_pca$CA$eig
sum(met_pca$CA$eig)
round(met_pca$CA$eig / met_pca$tot.chi, 2)
plot(met_pca)
biplot(met_pca)
cleanplot.pca(met_pca)
ordiplot(met_pca, display = 'met')
orditorp(met_pca, display = 'met')

met_mds <- metaMDS(metabolomics)
plot(met_mds)

plot(met_mds, type='n')
 text(met_mds, 'met', cex=.5)
 color_vect = rev(terrain.colors(6))[-1]
 points(met_mds, 'diet', pch=19, 
        col=color_vect[met.env$diet])
 legend('topright', paste("diet =", 1:5, sep=''), 
        col=color_vect, pch=19)
 
 rda_met <- rda(met, met.env)
 rda_met

 RsquareAdj(rda_met)
 
 plot(rda_met, type='n', scaling=1)
orditorp(rda_met, display='met', cex=0.5, scaling=1, col='blue')
text(rda_met, display='met', col='red')
```


ANOVA's for Proximate Analysis and bar plots of proximates
```{r}
#This code chunk will not have any data with it now; just the template for now until Clemson Feed and Forage Lab opens back up and can analyse my samples

protein <- table(proximates$protein)
barplot(protein, main="Protein comparison among diet treatments", 
   xlab="Diets")

fat <- table(proximates$fat)
barplot(fat, main="Fat comparison among diet treatments", 
   xlab="Diets")

carb <- table(proximates$carb)
barplot(carb, main="Carbohydrate comparison among diet treatments", 
   xlab="Diets")


```


Weekly Water Quality Range, mean, stdev for data table
```{r}
mean(water$`Ammonia mg/L`)
sd(water$`Ammonia mg/L`)
range(water$`Ammonia mg/L`)
mean(water$`Nitrite mg/L`, na.rm = TRUE)
sd(water$`Nitrite mg/L`, na.rm = TRUE)
range(water$`Nitrite mg/L`, na.rm = TRUE)
mean(water$`Nitrate mg/L`, na.rm = TRUE)
sd(water$`Nitrate mg/L`, na.rm = TRUE)
range(water$`Nitrate mg/L`, na.rm = TRUE)
```


Daily Water Quality Range, mean, stdev for data table
```{r}
mean(daily$temp)
sd(daily$temp)
range(daily$temp)
mean(daily$do, na.rm = TRUE)
sd(daily$do, na.rm = TRUE)
range(daily$do, na.rm = TRUE)
mean(daily$sal)
sd(daily$sal)
range(daily$sal)
mean(daily$pH)
sd(daily$pH)
range(daily$pH)


```